Column Comparison

### 2021-03-09 gc_column_comparison_2.Rmd
additional plots

# Overview Plot
```{r, fig.width=10, fig.height=6, warning=FALSE}
# Overview Plot
p_fames_db1 <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
    geom_bar(stat = 'identity', width = 0.1) +
    facet_grid(rows = vars(column_type), cols = vars(standard_ID), scales = "free_y") +
    ggtitle("FAME Standards Overview") +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_fames_db1
```

@@

```{r}
p_resolution <- peak_analysis %>% ggplot(aes(x = column_type, y = `Resolution (EP)`, fill = column_type)) +
  geom_boxplot() +
  facet_wrap(~standard_ID)+
  scale_fill_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2) +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              y_position = 40,
              textsize = 2) +
  xlab("Column Type") +
  ggtitle("FAME Peak Resolution") +
  theme_classic() +
  theme(legend.title = element_blank())
p_resolution
```

@@

```{r}
p_symmetry <- peak_analysis %>% ggplot(aes(x = column_type, y = `Asymmetry (EP)`, color = saturation)) +
  geom_point() +
  geom_jitter(width = 0.2, height = 0) +
  facet_wrap(~standard_ID)+
  scale_color_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              y_position = 4.1,
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  xlab("Column Type") +
  ggtitle("FAME Peak Asymmetry") +
  theme_classic() +
  theme(legend.title = element_blank())
p_symmetry
```

# Plates Plot
Significance testing via Wilcox Test

```{r}
p_plates <- peak_analysis %>% ggplot(aes(x = column_type, y = `Plates (EP)`, color = saturation)) +
  geom_point() +
  geom_jitter(width = 0.2, height = 0) +
  facet_wrap(~standard_ID)+
  scale_color_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              y_position = 6e6,
              color = "black") +
  xlab("Column Type") +
  ggtitle("FAME Plates") +
  theme_classic() +
  theme(legend.title = element_blank())
p_plates
```

@@

```{r}
p_retention <- peak_analysis %>% ggplot(aes(x = column_type, y = `Retention Time`, color = saturation)) +
  geom_point() +
  geom_jitter(width = 0.2, height = 0) +
  facet_wrap(~standard_ID)+
  scale_color_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black",
              y_position = 41) +
  xlab("Column Type") +
  ylab("Retention Time (Minutes") +
  ggtitle("FAME Retention Times") +
  theme_classic() +
  theme(legend.title = element_blank())
p_retention
```

>>>>

# Overview Plot
```{r, fig.width=10, fig.height=6, warning=FALSE}
# Overview Plot
p_fames_overview <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
    geom_bar(stat = 'identity', width = 0.1) +
    facet_grid(rows = vars(column_type), cols = vars(standard_ID), scales = "free_y") +
    ggtitle("FAME Standards Overview") +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_fames_overview
```

@@

```{r}
p_resolution <- peak_analysis %>% ggplot(aes(x = column_type, y = `Resolution (EP)`, color = saturation)) +
  geom_boxplot() +
  facet_wrap(~standard_ID)+
  scale_color_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              y_position = 40,
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  xlab("Column Type") +
  ggtitle("FAME Peak Resolution") +
  theme_classic() +
  theme(legend.title = element_blank())
p_resolution
```

Peak resolution distributions are more or less conserved across all column types.

@@

```{r}
p_symmetry <- peak_analysis %>% ggplot(aes(x = column_type, y = `Asymmetry (EP)`)) +
  geom_boxplot() +
  facet_wrap(~standard_ID)+
  scale_color_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              y_position = 4.1,
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  xlab("Column Type") +
  ggtitle("FAME Peak Asymmetry") +
  theme_classic() +
  theme(legend.title = element_blank())
p_symmetry
```

Not sure what to make of peak asymmetry metric. Most of the data hovers around 1, which I assume is a good sign that peaks do not have much tailing.

# Plates Plot
Significance testing via Wilcox Test.

```{r}
p_plates <- peak_analysis %>% ggplot(aes(x = column_type, y = `Plates (EP)`, color = saturation)) +
  geom_boxplot() +
  facet_wrap(~standard_ID)+
  scale_color_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              y_position = 6e6,
              color = "black") +
  xlab("Column Type") +
  ggtitle("FAME Plates") +
  theme_classic() +
  theme(legend.title = element_blank())
p_plates
```

DB1 has the highest theoretical plate count. This is not surprising since it is a 60m column and plates are proportional to column. Both DB5 and ZBFAMES are 30m column, and DB5 has significantly higher theoretical plate count.

@@

```{r}
p_retention <- peak_analysis %>% ggplot(aes(x = column_type, y = `Retention Time`, color = saturation)) +
  geom_jitter(width = 0.1, height = 0) +
  facet_wrap(~standard_ID)+
  scale_color_npg() +
  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black") +
  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
              textsize = 2,
              map_signif_level = TRUE,
              color = "black",
              y_position = 41) +
  xlab("Column Type") +
  ylab("Retention Time (Minutes") +
  ggtitle("FAME Retention Times") +
  theme_classic() +
  theme(legend.title = element_blank())
p_retention
```
Retention times for DB1 are much longer. DB5 and ZBFAMES are roughly similar.

# Average Peak Distancing

```{r}
# Mutate to give spacing based on previous peak RT
peak_analysis <- peak_analysis %>%
  group_by(sample) %>% 
  mutate(
  peak_spacing = `Retention Time` - lag(`Retention Time`))
peak_analysis_avg <- peak_analysis %>%
  group_by(sample) %>% 
  summarise(avg_peak_spacing = mean(peak_spacing, na.rm = TRUE))

# Plot
p_peak_spacing <- peak_analysis_avg %>%
  ggplot(aes(x = sample, y = avg_peak_spacing)) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90))
p_peak_spacing
```
This plot isn't telling me too much.

# Saturated Compound Elution

```{r, fig.width=10, fig.height=6, warning=FALSE}

c18points <- results$`Peak Name` %>% 
  str_subset("18")

p_fames37 <- results %>%
  filter(column_type %in% c("DB5", "ZBFAMES")) %>% 
  filter(standard_ID == "37FAME") %>% 
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
    geom_bar(stat = 'identity', width = 0.1) +
    facet_wrap(~column_type, ncol = 1) +
    ggtitle("37FAME DB5/ZBFAMES") +
    # Subset labels
    geom_label_repel(data = . %>% 
                       mutate(label = ifelse(`Peak Name` %in% c18points, `Peak Name`, "")),
                     aes(label = label),
                     show.legend = FALSE,
                     size = 2,
                     nudge_y = 7,
                     box.padding = 1) +
    coord_cartesian(ylim = c(0,11)) +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_fames37
